Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-04-06 chSiGaps/AO_bondedSi.tex
fix subfloat and figure sizes in SiGaps chapter.  looks good now!

\begin{figure}[htbp]
\includegraphics[width=0.40\columnwidth]{chSiGaps/figs/fpAbsorbfig_alt}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.40\columnwidth]{chSiGaps/figs/etalon_trans.pdf}
\caption{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', defined as the Absolute transmission through a sample normalized by the absolute transmission through a gapless sample. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0-3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\`erot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=1.0\columnwidth]{chSiGaps/figs/VS20fineGapCrop.pdf}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=0.4\columnwidth]{chSiGaps/figs/VS2021_IR_image.pdf}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\label{figVG03_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 hole region]{\label{figVG03_f100}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f100.pdf}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\label{figVG03p2_corner}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \newline
    \subfloat[Measured spectrum and fit of VG03 petal region]{\label{figVG03_f045}}
    	\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f045.pdf}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Illustration of VG09-12 sample transport accessory measurement positions.]{\label{figVG0912_STA_illus}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf}
    \subfloat[Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\label{figVG0912}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\label{VG0912_0gap_corner}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf}
    \subfloat[Measured spectrum of VG09-12]{\label{VG0912_0gap}}
        \includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap.pdf}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12-STA}}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.60\columnwidth]{chSiGaps/figs/fpAbsorbfig_alt}
\end{center}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\begin{center}
	\includegraphics[width=0.40\columnwidth]{chSiGaps/figs/etalon_trans.pdf}
\end{center}
\caption{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', defined as the Absolute transmission through a sample normalized by the absolute transmission through a gapless sample. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0-3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\`erot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{chSiGaps/figs/VS20fineGapCrop.pdf}
\end{center}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\columnwidth]{chSiGaps/figs/VS2021_IR_image.pdf}
\end{center}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \label{figVG03_corner}}
    	 \newline
    \subfloat[][Measured spectrum and fit of VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f100.pdf} \label{figVG03_f100}}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \label{figVG03p2_corner}}
    	\newline
    \subfloat[][Measured spectrum and fit of VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f045.pdf} \label{figVG03_f045}}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Illustration of VG09-12 sample transport accessory measurement positions.]{\includegraphics[width=0.3\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf} \label{figVG0912_STA_illus}}
    \newline
    \subfloat[][Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\includegraphics[width=0.8\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf} \label{figVG0912}}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf} \label{VG0912_0gap_corner}}
    \newline
    \subfloat[][Measured spectrum of VG09-12]{\includegraphics[width=0.65\textwidth]{chSiGaps/figs/VG0912_0gap.pdf} \label{VG0912_0gap}}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12-STA}}
\end{figure}
